Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-03 nlpcc/paper.tex
0601遗留的3个点

\subsection{Wiki Pages}
Articles from the four sources are similar in structure. Usually they provide two important elements with potential semantic information, category taxonomy and articles. A taxonomy presents the relations between categories. Usually a category has sub-categories and super-categories. Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy. An article describes an entity with rich information created and modified by several verified editors. Besides, each article is linked to one or more categories by \textit{articleOf} relation. In general, there are five elements can be exploited in each article page:
\begin{figure}
    \centering
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
        \caption{Taxonomy in Hudong}
        \label{fig:hudong-taxonomy}
    \end{minipage}%
\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article. 
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are subject-attribute-value triples formalized as a table. Information in this table includes important properties of an entity.
  \item Links: Links are entries to other articles within the encyclopedia. They lead readers to reference articles. Actually, they represent the relations between the current article and other articles.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article belongs to one or more categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

@@

However, the whole taxonomy can not directly transform from category system because of the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
    %s\item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one or two articles. According to the definition of concept, such categories are less representative to a group of instances, therefore it's unwise to retain it as concept.
\end{itemize}
   To obtain a more precise concept taxonomy,first remove such categories in all encyclopedias, and build the original concept hierarchy $H^C$ using the remaining categories.  
However, among the relations there are still incorrect samples. For example, \emph{Tsinghua University} is not an entity of \emph{Haidian District}, but relates to. Thus we will prune the taxonomy later.

@@

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from. When a dump label in triple-bracket occurs in dump file, we replace it by its mapping display label. After convert all the dump labels, we make a filter to redress the label text.

@@

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: (1) Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label. That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties; (2) Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; (3) Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity.

In order to make all these encyclopedias link to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers. For instance, we merge instances by the following method:

\begin{enumerate}[Step 1]
    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
    \item Other instances existing in only one encyclopedia are considered as independent instances. Up to now, we have combined all Chinese articles describing the same entity as one instance. Each instance may correspond to 1 to 3 sources.
    \item To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an new ID.
\end{enumerate}

>>>>

\subsection{Wiki Pages}
Articles from the four sources are similar in structure. Usually they provide two important elements with potential semantic information, category system and articles. A category system represents the relations between categories as a tree by the relation \textit{subCategoryOf}. Fig.\ref{fig:hudong-taxonomy} shows a screenshot of Hudong Taxonomy. An article describes an entity with rich information created and modified by several verified editors. Besides, each article is linked to one or more categories by \textit{articleOf} relation. In general, there are five elements can be exploited in each article page:
\begin{figure}
    \centering
    \begin{minipage}[t]{0.8\textwidth}
        \centerline{\includegraphics[width=0.8\columnwidth]{fig/hudong-taxonomy2}}
        \caption{Taxonomy in Hudong}
        \label{fig:hudong-taxonomy}
    \end{minipage}%
\end{figure}
\begin{itemize}
  \item Title: A Title is the label of an entity, which is unique so that it can be used to distinguish entities.
  \item Abstract: An abstract is a brief summary of the entity. It's always the first paragraph of an article. 
  \item Infobox: Most of articles contain infobox. An infobox maintains structured data which are subject-attribute-value triples formalized as a table. Information in this table includes important properties of an entity.
  \item Links: Links are entries to other articles within the encyclopedia. They lead readers to reference articles. Actually, they represent the relations between the current article and other articles.
  \item Category: The categories that an article belongs to are usually listed at the bottom of article page, shown as tags. An article has \textit{articleOf} relation with its categories.
  \item URL: Each article has an HTTP url to identify itself on web.
\end{itemize}

@@

However, the whole taxonomy can not directly transform from category system because of the following problems:
\begin{itemize}
    \item There are auxiliary categories in Wikipedia, which help arrange specific articles or category pages. For example, \emph{Lists of artists} or \emph{Food templates}.
    %s\item Some sub-category links in the category system maybe inconsistent. Some categories may contain itself as sub-category, or contain sub-category that also be the super-category of it. As Fig. \ref{fig:category-mistakes} shows: In Hudong, the sub-category of 国家元首(Head of State) contains itself as a child, which causes a circle in taxonomy tree. Meanwhile, in Wikipedia, \textcolor{red}{例子}
    \item Some categories relate to only one or two articles. According to the definition of concept, such categories are less representative to a group of instances, therefore it's unwise to retain it as concept.
\end{itemize}
   To obtain a more precise $H^C$ in a $W$, we remove such categories in all encyclopedias, then build the original concept hierarchy $H^C$ using the remaining categories.

However, among the relations there are still incorrect samples. For example, \emph{Tsinghua University} is not an entity of \emph{Haidian District}, but relates to. Thus we will prune the taxonomy later.

@@

To solve the problems above, we take advantage of template information. Specifically, Wikipedia institutes rules of rendering label in templates. For example, movie infobox follows template \emph{Infobox film}, which is shown on the right of Fig.\ref{fig:infobox-template}, where both display labels and dump labels come from. When a dump label occurs in dump file, we replace it by its mapping display label.

@@

However, due to using templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: 
\begin{enumerate}[1)]
    \item Given a matched template, which means $T_{e}$ and $T_{z}$ are cross-lingual pairs, find the display labels mapping the same dump label. That is to say, to two pairs, $p_{e}$ in $T_{e}$ and $p_{z}$ in $T_{z}$, if $tl_{e}$ is equal to $tl_{z}$, $<dl_{e},dl_{z}>$ are cross-lingual properties;
    \item Given the English and Chinese infoboxes of a matched instance, compare their templates, which are English template $T_{e}(a_{e})$ and a Chinese template $T_{z}(a_{z})$ in which $a_{e}$ and $a_{z}$ direct to the same entity, find the matched display labels mapping to the same dump label; 
    \item Given the English and Chinese infoboxes of a matched instance, for datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity. 
\end{enumerate}

In order to make all these encyclopedias link to each other, we unify the same concept, instance and property from four sources, and give them unique identifiers. For instance, we merge instances by the following method: (1) Merge all instances extracted from Chinese encyclopedias by instance title. (2) To a $L_{z}(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID, else number it with an new ID.
